Postural developments mediate children's visual access to social information

### 2018-01-24 writeup-cogsci/cogsci2018_faceOnly.Rmd
adding detector text again?

### Detector evaluation

@@

  select(-angle) %>%
  arrange(video, frame) %>%
  cbind(read_csv("../data/ground_truth/gold_set_candidates2.csv") %>%
          arrange(video, frame) %>%
          select(sample_type))

>>>>

### Detector evaluation
To evaluate detector performance, we constructed a "gold set" of frames by hand labeling both a sample of frames with a high density of faces (half reported by the MTCNN, half by OpenPose) and a random sample from the remaining frames; each sample was comprised of frames sampled from each participant (i.e., video). This was done so as to not bias our evaluation by the relatively rare appearance of faces in the dataset.  Faces were classifed as present in a frame if at least half of the face was showing. Precision (hits / hits + false alarms), recall (hits / hits + misses), and F-score (harmonic mean of previous measures) were calculated for all detectors and are reported in Table 2.

Both OpenPose and MTCNN detectors performed relatively well on the gold set, with MTCNN outperforming OpenPose on the random sample but trailing behind in the high density sample. We found a clear tradeoff between recall and precision between the two models. That is, MTCNN almost always detected a face if it was present, but made more false alarms; conversely, OpenPose made less false alarms but overall detected fewer faces. ViolaJones performed quite poorly, missing many of the faces in the randomly sampled frames.

@@

ground_truth_data <- read_csv("../data/ground_truth/ground_truth4.csv") %>%
  select(-angle) %>%
  arrange(video, frame) %>%
  cbind(read_csv("../data/ground_truth/gold_set_candidates2.csv") %>%
          arrange(video, frame) %>%
          select(sample_type))
